Individualized Measures of Partisan Fairness and Utility in Redistricting (??)

### 2021-08-30 paper/paper.Rmd
add informal line
better connect utility and harm

To operationalize this, we need to introduce a counterfactual districting plan $\tilde q$.
Then we may define the harm to a voter as$$
    h:\Voters\times\Elecs\times\Plans^2\to\R, 
    \qquad h(v,e,q,\tilde q) = 
        \ind\{\vote(v, e)\neq\win(q(v), e, q)\}
        \ind\{\vote(v, e)=\win(\tilde q(v), e, \tilde q)\},
$$that is, a voter is harmed only if they are not represented by the party of their choice *and* they would have been represented by the party of their choice under the counterfactual plan.

@@

Continuing with the above notation, the average fairness of $Q$ versus counterfactual $\tilde Q$ may be defined as $$
    F = \E[H\mid \vote(V, E) = A] - \E[H\mid \vote(V, E) = B];
$$obviously the ordering of $A$ and $B$ is immaterial.

>>>>

To operationalize this, we need to introduce a counterfactual districting plan $\tilde q$.
Then we may define the harm to a voter as $h:\Voters\times\Elecs\times\Plans^2\to\R$, \begin{align*}
    h(v,e,q,\tilde q) &= (1 - u^{(L)}(v, e, q))\cdot u^{(L)}(v, e, \tilde q) \\
    &= \ind\{\vote(v, e)\neq\win(q(v), e, q)\}
        \ind\{\vote(v, e)=\win(\tilde q(v), e, \tilde q)\},
\end{align*}that is, a voter is harmed only if they are not represented by the party of their choice *and* they would have been represented by the party of their choice under the counterfactual plan.

@@

Continuing with the above notation, the average fairness of $Q$ versus counterfactual $\tilde Q$ may be defined as $$
    F = \E[H\mid \vote(V, E) = A] - \E[H\mid \vote(V, E) = B];
$$obviously the ordering of $A$ and $B$ is immaterial.
Informally, this quantity is the difference in the probability that a voter of each party is represented by the other party but counterfactually would have been represented by their own party.
